At that moment, Ada's aunt, Emily, comes out of the house.\\
"Hello Ada," says Emily, "how are you?"\\
"Emily!" Ada exclaims.\\
Ada really likes Emily. She is one of her favorite aunts.
Emily is very cool; she has traveled a lot and speaks three different languages. And, her job is to build rockets!\\
"Look, Emily, I'm playing with numbers!" Ada explains. "I've drawn all the numbers from $0$ to $9$. And when I take a step forward, I move on to the next one. And when I take a step backwards, I return to the previous one." \\
Emily then explained to Ada that when she takes a step forward, she adds one to the number she was on and that you draw $+1$. When she takes a step backwards, she subtracts one from the number she was on and you draw $-1$. Ada now has two new symbols to use: plus ($+$) for addition and minus ($-$) for subtraction. She thinks that these two new symbols are fun. Ada and Emily decide to play together. Starting from $0$, Ada takes three steps forward ($+3$) and then one step back ($-1$). Now she's at $2$. Emily takes out a notebook and a pencil and shows Ada how to draw her path: $0 + 3 - 1$. And as Ada is now on $2$, Emily explains that there is a symbol called equal ($=$), which is used to say that she has arrived at $2$: $0 + 3 - 1 = 2$. Ada thinks it sounds like a magic formula. She really wants to try it again. \\
"Come on, Auntie, you write the numbers and funny symbols in your magic notebook and I'll go along the line."\\
Emily showed her her notebook where it said: $4 + 3 - 2$. Ada thought about it. \\
"You have to start at $4$, take three steps forward and two back, right?" \\
"That's it!" replied Emily. \\
So Ada set off. Starting from $4$, she took three steps forward and arrived at $7$.
Then she turns and takes two steps in the other direction. Ada is now on number $5$. Emily notes $4 + 3 - 2 = 5$.\\
"Now it's my turn," Ada shouts.\\
Emily gives her her notebook and pencil and Ada writes: $1 + 7 - 3$. Emily looks at the paper, gets up and walks over to number $5$.
"Voilà!", she said, and write $1 + 7 - 3 = 5$ in the notebook.\\
"What?" asks Ada. "You're cheating! You have to start from $1$, take seven steps forward and three back."\\
And Ada showed her. She stood on the $1$, took seven steps forward (she was now on the $8$) and then took three steps back to arrive exactly where Emily was, on the number $5$.
Emily then explained to Ada that, thanks to the notebook and pencil, you don't always have to go back and forth. You can calculate the result of operations (that's what Emily calls the magic the magic formulae with the digits, the $+$ and the $-$) and find out the result (what comes after the $=$) without even moving. Ada is sceptical. She asks Emily for another example. Emily stands on the $0$ and writes down $2 + 4 - 5 + 2 - 3$ in her notebook. Ada stands on the $2$, takes four steps forward, then five in the other direction, turns around and takes two steps forward and three steps back. Phew! She almost felt dizzy. Emily didn't move. Ada looked down at her feet and saw the $0$. Emily smiled at her and wrote $2 + 4 - 5 + 2 - 3 = 0$.\\
"You see," she says, "I knew we'd both end up here on $0$, even before you started." \\
"It's true," replies Ada, "it's handy for those really long formulas that make you dizzy. But I think it's more fun to travel for real!"