While Emily picks salad, Ada and Charles play "Ada says" together. The aim is simple: Ada gives Charles orders, and Charles must carry them out only if Ada says "Ada said".\\
"Ada said, take three steps back!"\\
Charles does indeed take three steps back.\\
"Bravo! Ada said, hop on one foot!"\\
Charles stands on one foot and begins to hop.\\
"Now run forward five steps."\\
Not holding back, Charles starts running toward Ada.\\
"Lost! I didn't say "Ada said"."\\
"Oh, no, you didn't! Come on, it's my turn! Charles said $3 \times (-2)$."\\
"$3 \times (-2)$!? Wait a minute..." Ada thinks about it and says: "$2$ means you take two steps back, so $3 \times (-2)$ means you take three two-step steps back."\\
Ada takes six steps back.
"Charles said $(-2) \times 3$!"\\
Ada takes six steps back again.\\
"Hey, you're cheating!" exclaims Charles.\\
"How am I cheating?" replies Ada.\\
"Yes, you are! Before it was $3 \times (-2)$ and now it's $(-2) \times 3$, so it's not the same."\\
"$(-2) \times 3$ is to take two steps back three times, it's like taking two steps back three times. $3 \times (-2) = (-2) \times 3$."\\
Just then, Emily arrives with a salad in each hand.\\
"Ada is right. Multiplication is commutative."\\
"Commuta-what?" ask the siblings in chorus.\\
"Commutative. This means that you can change the place of the numbers around the $\times$ sign: $5 \times 4 = 4 \times 5$, $7 \times 3 = 3 \times 7$, or even $3 \times (-2) = (-2) \times 3$. It also works for addition: $1 +3 = 3 + $1, $5 + 2 = 2 + 5$."\\
What about subtraction and division?" asks Ada.\\
"They're not commutative. You can't move the numbers around as you like: $3 - 2$ doesn't equal $2 - 3$ and $6/3$ doesn't equal $3/6$."\\
Ada looks at Charles.\\
"That means I've won!"\\
"No, one more. Charles said $(-4) \times (-3)$!"\\
Ada thinks. She's never multiplied two negative numbers before.\\
"When you take two steps forward, you write $2$ and when you take two steps back, you write $(-2)$. If we had $4 \times (-3)$, four packets of $(-3)$, we'd go back four times by three steps."\\
Ada calculates. \\
"We'd go back 12 steps. And since we have $(-4) \times (-3)$, we do the same thing in the other direction. We'd take 12 steps forward."\\
Ada asks Emily.\\
"Say, Auntie, is $(-4) \times (-3)$ equal to $12$?\\
"Bravo Ada," replies Emily, "when you do multiplication with positive and negative numbers, you have to juggle with the signs."\\
"Juggling with signs? Sounds difficult."\\
"No, you just did it. Multiplying two positive numbers together or two negative numbers together always gives a positive result. Multiplying a positive number with a negative number gives a negative result."\\
Suddenly, a voice from the house calls out to the children:\\
"Ada, Charles! It's time to go home!"\\
"We're coming!" the siblings answer in unison.